---
title: "Introduction to StatComp22064"
author: "Shiqi Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp22064}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22064__ is a simple R package developed to compare the performance of R and C++ (implemented through the R package _Rcpp_) for the 'Statistical Computing' course. Two functions are considered, namely, _gibbs_ (generate for two-dimensional normal random numbers using Gibbs sampler) and _shortest_ (calculate the shortest path problem between cities). For each function, both R and Rcpp versions are produced. Namely _gibbsR_ and  _shortestR_ for R and _gibbsC_ and _shortestC_ for C++.

The R package 'microbenchmark' can be used to benchmark the above R and C++ functions.

## Benchmarking _shortestR_ and _shortestC_

The source R code for _shortestR_ is as follows:
```{r,eval=FALSE}
shortestR <- function(M){
  n<-max(M)
  A<-matrix(Inf,n,n)
  for(i in 1:nrow(M)){A[M[i,1],M[i,2]]<-A[M[i,2],M[i,1]]<-1}
  diag(A)<-0
  
  while(TRUE){
    B<-A
    for(i in 1:n){
      for(j in 1:n){
        for(k in 1:n){
          if(A[i,j]>A[i,k]+A[k,j]){
            A[i,j]<-A[i,k]+A[k,j]
          }
        }
      }
    }
    if(identical(B,A)){break}else{B<-A}
  }
  return(A)
}
```

The above code involves multiple "for" loops which will take a lot of time to compute in R. On the other hand, the following _Rcpp_ code is much faster.

```{r,eval=FALSE}
NumericMatrix shortestC(NumericMatrix M){
  M=M-1; 
  int n=max(M(_,1))+1; 
  NumericMatrix A(n,n);
  A.fill(R_PosInf);
  A.fill_diag(0);
  for(int i=0;i<M.nrow();i++){
    A(M(i,0),M(i,1))=1;
    A(M(i,1),M(i,0))=1;
  }
  
  while(true){
    NumericMatrix B=clone(A);
    for(int i=0;i<n;i++){
      for(int j=0;j<n;j++){
          for(int k=0;k<n;k++){
            if(A(i,j)>A(i,k)+A(k,j)){
              A(i,j)=A(i,k)+A(k,j);
            }
          }
      }
    }
    if(sum(A!=B)==0){break;}else{B=clone(A);}
  }
  return A;
}
```

In order to empirically benchmark _shortestR_ and _shortestC_, one generates generate a matrix M containing 100 city connectivity information, and save it in data{StatComp22064}. To load the file, one simply calls _data(data)_. The R code for benchmark _shortestR_ and _shortestC_ is as follows.

```{r,eval=TRUE}
library(StatComp22064)
library(microbenchmark)
data(data)
tm2 <- microbenchmark(
  shortestR = shortestR(M),
  shortestC = shortestC(M)
)
knitr::kable(summary(tm2)[,c(1,3,5,6)])
```

The above results show an evident computational speed gain of C++ against R.


## Benchmarking _gibbsR_ and _gibbsC_

The source R code for _gibbsR_ is as follows:
```{r,eval=FALSE}
gibbsR <- function(N, mu1, mu2, sigma1, sigma2, pho) {
  mat <- matrix(nrow = N, ncol = 2)
  x <- 0
  y <- 0
  s1 = sqrt(1-pho * pho) * sigma1
  s2 = sqrt(1-pho * pho) * sigma2
  for (i in 1:N) {
    m1 = mu1 + pho * (y - mu2) * sigma1 / sigma2;
    x = rnorm(1, m1, s1);
    mat[i, 1] = x;
    
    m2 = mu2 + pho * (x - mu1) * sigma2 / sigma1;
    y = rnorm(1, m2, s2);
    mat[i, 2] = y;
  }
  mat
}
```

The above R code involves two loops, which could be very slow even for R-3.01 or any higher version. The corresponding C++ code is as follows.

```{r,eval=FALSE}
NumericMatrix gibbsC(int N, double mu1, double mu2, double sigma1, double sigma2, double pho) {
  NumericMatrix mat(N, 2);
  double s1 = sqrt(1-pho * pho) * sigma1, s2 = sqrt(1-pho * pho) * sigma2;
  double x = 0, y = 0;
  for(int i = 0; i < N; i++) {
    double m1 = mu1 + pho * (y - mu2) * sigma1 / sigma2;
    x = rnorm(1, m1, s1)[0];
    mat(i, 0) = x;

    double m2 = mu2 + pho * (x - mu1) * sigma2 / sigma1;
    y = rnorm(1, m2, s2)[0];
    mat(i, 1) = y;
  }
  return(mat);
}
```

The R code for benchmarking _gibbsR_ and _gibbsC_ is as follows.

```{r,eval=TRUE}
tm2 <- microbenchmark(
  vR = gibbsR(N=2000, mu1=0, mu2=0, sigma1=1, sigma2=1, pho=0.9),
  vC = gibbsC(N=2000, mu1=0, mu2=0, sigma1=1, sigma2=1, pho=0.9)
)
knitr::kable(summary(tm2)[,c(1,3,5,6)])
```

The results again show an evident computational speed gain of C++ against R.

